---
title: "Annual temperature trends by hemishpere"
author: "collnell"
date: "July 4, 2016"
output: html_document
---

```{r,include=F}
library(reshape2)
library(dygraphs)


setwd("/Users/colleennell/Documents/R/GISTEMP/")
data<-read.csv("hemtemps.csv")
tryd<-data[,c(1,3,4)]
tryd[,3]<-(tryd[,3])/10
tryd[,2]<-(tryd[,2])/10
```

```{r,thefig,echo=F}
dygraph(tryd)%>%
  dySeries("NHem",label="Northern Hemisphere")%>%
  dySeries("SHem",label="Southern Hemisphere")%>%
  dyLegend(width=400)%>%
  dyRangeSelector(strokeColor="black",fillColor="grey")%>%
  dyHighlight(highlightSeriesOpts=list(strokeWidth=3))%>%
  dyLimit(0,color=)
```
  
  These data show long term temperature patterns for the Northern and Southern Hemispheres. Dates on the x-axis are the time period pictured, and y-axis values indicate how much warmer (or colder if negative) temperatures were relative to normal. Baseline temperatures are based on averages from 1951-1908 and indicated by the red dashed line at 0.  Use time range selector below the x-axis to change the visible temperature range in the plot.
  
  
These data show that since the 1980's temperatures in the Southern Hemisphere are increasing at a lower rate than temperatures int he Northern Hemisphere. This is likely due to the high proportion of ocean in the Southern Hemisphere relative to the Northern Hemisphere.       
<br>  
  **Data Source:**  
  GISTEMP Team, 2016: GISS Surface Temperature Analysis (GISTEMP). NASA Goddard Institute for Space Studies. Dataset accessed 20YY-MM-DD at http://data.giss.nasa.gov/gistemp/.  
+ Hansen, J., R. Ruedy, M. Sato, and K. Lo, 2010: Global surface temperature change, Rev. Geophys., 48, RG4004, doi:10.1029/2010RG000345.  
<br>